Finite-state morphological transducers for three Kypchak languages

### 2013-10-11 kipchak-lrec-2013/kipchak-paper.tex
updates and fixes
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@48029 72bbbca6-d526-0410-a7d9-f06f51895060

\documentclass{article}

\usepackage{fontspec}
\usepackage{xunicode}
\usepackage{xltxtra}
\usepackage{natbib}
\usepackage{multirow}
\usepackage{fullpage}
\usepackage{multirow}

@@

\setromanfont{DejaVu Serif}

@@

@@

\maketitle

\begin{abstract}
Hargle, bargle.
\end{abstract}

@@

\bibliographystyle{apalike}

\bibliography{kipchak-paper}

>>>>

\documentclass[a4paper,11pt,twocolumn]{article}

\usepackage{lrec2012}

\usepackage{polyglossia}
\setdefaultlanguage[variant=australian]{english}

\usepackage{fontspec}
\usepackage{xunicode}
\usepackage{xltxtra}
\usepackage{natbib}
\usepackage{multirow}
%\usepackage{fullpage}
\usepackage{multirow}

@@

\setromanfont{Times New Roman}

@@

\name{Jonathan North Washington, Ilnar Salimzyanov, Francis M. Tyers}

\address{Departments of Linguistics and Central Eurasian Studies\\
Indiana University\\
Bloomington, IN 47405 (USA)\\
\texttt{jonwashi@indiana.edu} \and
Institut für Maschinelle Sprachverarbeitung \\
Universität Stuttgart\\
Stuttgart (Germany) \\
\texttt{ilnar@ilnar} \and 
Departament de Llenguatges i Sistemes Informàtics \\  
Universitat d'Alacant\\
E-03071 Alacant (Spain)\\
\texttt{ftyers@dlsi.ua.es} 
}

\abstract{Hargle, bargle.\\
\Keywords{Kazakh, Tatar, Kumyk, morphology, transducer}}

@@

\maketitleabstract{}

@@

\bibliographystyle{lrec2012}
\bibliography{kipchak-paper}
